Rank Verification in Exponential Families

### 2017-07-30 slides.tex
poster added, figures now in pdf

\begin{frame}{A na\"ive approach}
\begin{itemize}
\item Verifying winner as best: One-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: One-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure.
\end{itemize}
\end{frame}

\begin{frame}{A valid, yet simple, approach}
\begin{itemize}
\item Verifying winner as best: {\bf Two}-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: {\bf Two}-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a step-down procedure
\end{itemize}
\end{frame}

@@

\begin{frame}{Power comparison}
\centering
\includegraphics[width=0.95\textwidth]{multinomial-power.png}
\end{frame}

>>>>

\begin{frame}{A na\"ive approach}
\begin{itemize}
\item Verifying winner as best: One-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: One-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a stepwise procedure.
\end{itemize}
\end{frame}

\begin{frame}{A valid, yet simple, approach}
\begin{itemize}
\item Verifying winner as best: {\bf Two}-tailed level-$\alpha$ test comparing Trump to Cruz
\item By how much: Invert the test above
\item Verifying other ranks: {\bf Two}-tailed level-$\alpha$ test comparing first runner-up to second runner-up, etc., using a stepwise procedure
\end{itemize}
\end{frame}

@@

\begin{frame}{Power comparison}
\centering
\includegraphics[width=0.95\textwidth]{multinomial-power.pdf}
\end{frame}
